%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Mikkel Laursen} % Your name
\address{Lakewood, CO 80227} % Your address
\address{(804)~$\cdot$~380~$\cdot$~7418 \\ mlaursen03@gmail.com} % Your phone number and email

\begin{document}


%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}

Full stack developer but mostly front end now with an interest and focus on web accessibility and creating reusable components in React. 3+ years experience writing React and SCSS, 3+ years experience with Java EE, Oracle/Microsoft SQL databases, and JSP/JSF pages.

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Four Winds Interactive}{Jan 2018 - Present}{Senior Software Developer/Tech Lead}{Denver, CO}
\item Leading the front end team for technical decisions and general mentoring
\item Implementing and maintaining an in-house component library to meet the UX and Design requirements
\item Developing and maintaining other shared libraries for the front end applications
\item Developing and maintaining our Library web application which allows users to upload/manage assets for our digital signs
\item Working closely with the UX and Design team to create user friendly web applications
\item Working closing with the QA automation team to ensure our apps are testable by Selenium and notifying them of any changes
\item Introduced Google analytics and implemented general analytics across all our web applications using Segment and Hotjar
\item Migrated our front end apps from a custom webpack build to a custom fork of create-react-app for consistent builds
\end{rSubsection}

\begin{rSubsection}{Four Winds Interactive}{June 2016 - Jan 2018}{Software Developer}{Denver, CO}
\item Started the new CLOUD project to implement a mobile first/responsive web interface using React instead of Backbone.js 
\item Introduced automated tests into the normal FE development pipeline using jest
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{TEDS, Inc.}{May 2016 - June 2016}{Senior Software Engineer}{Blacksburg, VA}
\item Lead a team of 3 for a succession project written in React and Flux.
\item Developed and implemented an auto-generating javascript api from a Restful API's data/links.
\end{rSubsection}

\begin{rSubsection}{TEDS, Inc.}{March 2014 - June 2016}{Software Engineer}{Blacksburg, VA}
\item Maintained and developed the main LMS system written in Java and Java Server Pages.
\item Maintained and redesigned the external recruitment site using Primefaces and Java Server Faces.
\item Developed and updated a C utility for upgrading databases and setting application privileges by amazing guesswork.
\item Updated and developed on the main project's ant build script.
\item Updated and maintained database update scripts.
\item Updated and maintained a java util to export job statuses into a csv file.
\item Developed a client facing restful web service for accessing and maintaining education.
\item Designed and implemented a compile time annotation processor to generate a standalone test page for the new web services.
\item Lead, designed, and developed a Java CRUD API framework for automagically generating GET, POST, PUT, DELETE request for any Database Entity during a work hackathon.
\item Implemented a new Dashboard application by optimizing and rewriting slow queries and built a new front end with React, Flux, bootstrap, and sass.
\item Maintained and developed the Dashboard application build process using gulp.
\item Rewrote a stalled 6 month project in 3 weeks using React and material design as inspiration.
\item Implementing a modularized code base by moving all our projects into a single repository and using maven to create the distributables.
\item Maintaining the front end build tools using webpack and npm.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{CGI}{June 2013 - March 2014}{Consultant}{Lebanon, VA}
\item Front end development for an Oracle APEX website using jQuery.
\item Developed and documented tax forms in Java for the North Carolina Department of Revenue.
\end{rSubsection}

%-----------------------------------------------

\begin{rSubsection}{SMIPO}{January 2012 - January 2013}{Directory of Information Technology}{Radford, VA}
\item Maintained and designed the Joomula website for keeping track of stock changes.
\item Migrated the Joomula website to WordPress.
\end{rSubsection}

%-----------------------------------------------

\begin{rSubsection}{Richmond Public Schools}{June 2012 - August 2012}{Intern Web Developer}{Richmond, VA}
\item Researched and implemented a DotNetNuke module for file sharing named DMX.
\item Implemented a script to rename files for human readability and then move the files to the correct location on the web server.
\item Developed a Java application to parse the sitemap data to alert the web team when a website has not been updated within a year's time so that it can be removed.
\end{rSubsection}

%-----------------------------------------------

\begin{rSubsection}{Richmond Public Schools}{June 2011 - August 2011}{Intern}{Richmond, VA}
\item Created a dataflow for IT fix-its using Microsoft SharePoint.
\item Created new forms on Microsoft InfoPath to replace the forms written in COBOL.
\item Assisted with web maintenance and migration to ASP.net.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Radford University} \hfill {\em June 2013} \\ 
B.S. in Computer Science \& Engineering with a Dual Concentration in Database and Software Engineering \\
Completed 3 Independent Studies and 3 team projects that delivered a product to real clients. \\
Overall GPA: 3.43

\end{rSection}



%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

{\bf React Material Design - react-md} \hfill {\em January 2016 - Present} \\ 

A material design UI components library using React and sass. A live demo of the documentation can be viewed at https://react-md.mlaursen.com \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & JavaScript, Typescript, Java, bash \\
Databases & Oracle, PostgreSQL, Microsoft SQL \\
Tools & vim, git, yarn, npm \\
Other & React, Redux, webpack, node
\end{tabular}


\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
